---
title: "TOD_Myelin"
author: "Bosi Chen"
date: "7/20/2021"
output: html_document
---

```{r setup, include=FALSE}
library(float)
library(tidyverse)
library(knitr)
library(kableExtra)
library(plyr)
library(dplyr)
library(ggplot2)
library(ppcor)
library(psych)
library(tableone)
library(pander)
library(sjPlot)
library(sjmisc)
library(sjlabelled)

options(digits = 4, scipen = 999)

knitr::opts_chunk$set(warning=FALSE, message=FALSE, error = FALSE)
```

```{r, data-readin, include=FALSE, echo=FALSE, warning=FALSE}
# Read in dataset
rm(list=ls()) ## clear the workspace
#dev.off() ## Clear the plots
mypath <- file.path("/Users/bosi/OneDrive_SDSU/JDP/projects/toddler/TOD_Myelin")
TOD_Myelin_aparc = read.csv("/Users/bosi/OneDrive_SDSU/JDP/projects/toddler/TOD_Myelin/Toddler_Myelin_aparc_2020July.csv", na.strings = c("", "NA"), header = TRUE)
TOD_Myelin_aparc$Group <- factor(TOD_Myelin_aparc$Group) #1=ASD, 0=TD
TOD_Myelin_aparc$Sex <- factor(TOD_Myelin_aparc$Sex) #1=Female, 0=Male
TOD_Myelin_aparc_ASD <- TOD_Myelin_aparc[which(TOD_Myelin_aparc$Group==1),]
TOD_Myelin_aparc_TD <- TOD_Myelin_aparc[which(TOD_Myelin_aparc$Group==0),]
```

#GLM analysis 
<!-- ##T1/T2 ratio by Dx, age, and age by Dx interactions controlling for sex and CNR  -->
<!-- ```{r, GLM of T1/T2 ratio by Dx age and age by Dx interaction, echo = FALSE, include = TRUE, results='asis'} -->
<!-- n <-13 -->
<!-- T1T2ratio_aparc <- TOD_Myelin_aparc[,c(10:22)] -->
<!-- T1T2ratio_aparc_Vars = names(T1T2ratio_aparc) -->
<!-- T1T2ratio_glm <- lapply(1:n, function(x) lm(T1T2ratio_aparc[,x] ~ Age + Group + Sex + gray_white_cnr + Age*Group, data=TOD_Myelin_aparc)) -->

<!-- for (i in seq_along(T1T2ratio_aparc_Vars)) { -->
<!--   cat(tab_model(T1T2ratio_glm[i], dv.labels = paste(T1T2ratio_aparc_Vars[[i]]))$knitr,"\n--------\n") -->
<!-- } -->

<!-- ``` -->

##T1/T2 ratio by Dx, age, and age by Dx interactions without covariates
```{r, GLM of T1/T2 ratio by Dx age and age by Dx interaction without covariates, echo = FALSE, include = TRUE, results='asis'}
n <-13
T1T2ratio_aparc <- TOD_Myelin_aparc[,c(10:22)]
T1T2ratio_aparc_Vars = names(T1T2ratio_aparc)
T1T2ratio_glm_withoutcovariate <- lapply(1:n, function(x) lm(T1T2ratio_aparc[,x] ~ Age + Group + Age*Group, data=TOD_Myelin_aparc))
 
for (i in seq_along(T1T2ratio_aparc_Vars)) {
  cat(tab_model(T1T2ratio_glm_withoutcovariate[i], dv.labels = paste(T1T2ratio_aparc_Vars[[i]]))$knitr,"\n--------\n")
}

```

<!-- ##T1/T2 ratio by Dx, age, and age by Dx interactions controlling for sex, CNR, and TBV  -->
<!-- ```{r, GLM of T1/T2 ratio by Dx age and age by Dx interaction control for TBV, echo = FALSE, include = TRUE, results='asis'} -->
<!-- n <-13 -->
<!-- T1T2ratio_aparc <- TOD_Myelin_aparc[,c(10:22)] -->
<!-- T1T2ratio_aparc_Vars = names(T1T2ratio_aparc) -->
<!-- T1T2ratio_glm_tbv <- lapply(1:n, function(x) lm(T1T2ratio_aparc[,x] ~ Age + Group + Sex + gray_white_cnr + TBV + Age*Group, data=TOD_Myelin_aparc)) -->

<!-- for (i in seq_along(T1T2ratio_aparc_Vars)) { -->
<!--   cat(tab_model(T1T2ratio_glm_tbv[i], dv.labels = paste(T1T2ratio_aparc_Vars[[i]]))$knitr,"\n--------\n") -->
<!-- } -->

<!-- ``` -->


<!-- ##T1/T2 ratio by Dx and age controlling for sex and CNR  -->
<!-- ```{r, GLM of T1/T2 ratio by Dx and age, echo = FALSE, include = TRUE, results='asis'} -->
<!-- n <-13 -->
<!-- T1T2ratio_aparc <- TOD_Myelin_aparc[,c(10:22)] -->
<!-- T1T2ratio_aparc_Vars = names(T1T2ratio_aparc) -->
<!-- T1T2ratio_glm_simple <- lapply(1:n, function(x) lm(T1T2ratio_aparc[,x] ~ Age + Group + Sex + gray_white_cnr, data=TOD_Myelin_aparc)) -->

<!-- for (i in seq_along(T1T2ratio_aparc_Vars)) { -->
<!--   cat(tab_model(T1T2ratio_glm_simple[i], dv.labels = paste(T1T2ratio_aparc_Vars[[i]]))$knitr,"\n--------\n") -->
<!-- } -->

<!-- ``` -->

<!-- ##T1/T2 ratio by age in TD controlling for sex and CNR  -->
<!-- ```{r, GLM of T1/T2 ratio by age in TD, echo = FALSE, include = TRUE, results='asis'} -->
<!-- n <-13 -->
<!-- T1T2ratio_aparc_TD <- TOD_Myelin_aparc_TD[,c(10:22)] -->
<!-- T1T2ratio_aparc_Vars = names(T1T2ratio_aparc_TD) -->
<!-- T1T2ratio_age_TD <- lapply(1:n, function(x) lm(T1T2ratio_aparc_TD[,x] ~ Age + Sex + gray_white_cnr, data=TOD_Myelin_aparc_TD)) -->

<!-- for (i in seq_along(T1T2ratio_aparc_Vars)) { -->
<!--   cat(tab_model(T1T2ratio_age_TD[i], dv.labels = paste(T1T2ratio_aparc_Vars[[i]]))$knitr,"\n--------\n") -->
<!-- } -->

<!-- ``` -->

##Correlational plots of T1/T2 ratio with age 
```{r, correlational plots T1/T2 ratio with age, echo = FALSE, include = TRUE}

ggplot(TOD_Myelin_aparc, mapping = aes(x = Age, y = pericalcarine_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()
ggplot(TOD_Myelin_aparc, mapping = aes(x = Age, y = cuneus_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()
ggplot(TOD_Myelin_aparc, mapping = aes(x = Age, y = precuneus_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()
ggplot(TOD_Myelin_aparc, mapping = aes(x = Age, y = parahippocampal_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()
ggplot(TOD_Myelin_aparc, mapping = aes(x = Age, y = lingual_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()
ggplot(TOD_Myelin_aparc, mapping = aes(x = Age, y = isthmuscingulate_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()
ggplot(TOD_Myelin_aparc, mapping = aes(x = Age, y = transversetemporal_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()
ggplot(TOD_Myelin_aparc, mapping = aes(x = Age, y = lateraloccipital_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()
ggplot(TOD_Myelin_aparc, mapping = aes(x = Age, y = postcentral_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()
ggplot(TOD_Myelin_aparc, mapping = aes(x = Age, y = posteriorcingulate_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()
ggplot(TOD_Myelin_aparc, mapping = aes(x = Age, y = paracentral_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()
ggplot(TOD_Myelin_aparc, mapping = aes(x = Age, y = precentral_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()
ggplot(TOD_Myelin_aparc, mapping = aes(x = Age, y = superiorparietal_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()

```

<!-- ##T1/T2 ratio by Dx, maternal education, and Dx by maternal education interactions controlling for age  -->
<!-- ```{r, GLM of T1/T2 ratio by Dx maternal edu and Dx by maternal edu interaction control for age, echo = FALSE, include = TRUE, results='asis'} -->
<!-- n <-13 -->
<!-- T1T2ratio_aparc <- TOD_Myelin_aparc[,c(10:22)] -->
<!-- T1T2ratio_aparc_Vars = names(T1T2ratio_aparc) -->
<!-- T1T2ratio_matedu_glm <- lapply(1:n, function(x) lm(T1T2ratio_aparc[,x] ~ Group + maternal_edu + Age + Group*maternal_edu, data=TOD_Myelin_aparc)) -->

<!-- for (i in seq_along(T1T2ratio_aparc_Vars)) { -->
<!--   cat(tab_model(T1T2ratio_matedu_glm[i], dv.labels = paste(T1T2ratio_aparc_Vars[[i]]))$knitr,"\n--------\n") -->
<!-- } -->

<!-- ``` -->

##T1/T2 ratio by maternal education controlling for age and Dx 
```{r, GLM of T1/T2 ratio by maternal edu control for age and Dx, echo = FALSE, include = TRUE, results='asis'}
n <-13
T1T2ratio_aparc <- TOD_Myelin_aparc[,c(10:22)]
T1T2ratio_aparc_Vars = names(T1T2ratio_aparc)
T1T2ratio_matedu_glm_simple <- lapply(1:n, function(x) lm(T1T2ratio_aparc[,x] ~maternal_edu + Group + Age, data=TOD_Myelin_aparc))
 
for (i in seq_along(T1T2ratio_aparc_Vars)) {
  cat(tab_model(T1T2ratio_matedu_glm_simple[i], dv.labels = paste(T1T2ratio_aparc_Vars[[i]]))$knitr,"\n--------\n")
}

```

##Correlational plots of T1/T2 ratio with maternal edu 
```{r, correlational plots T1/T2 ratio with maternal edu, echo = FALSE, include = TRUE}

ggplot(TOD_Myelin_aparc, mapping = aes(x = maternal_edu, y = transversetemporal_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()
ggplot(TOD_Myelin_aparc, mapping = aes(x = maternal_edu, y = parahippocampal_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()
```

##T1/T2 ratio by ADOS CSS controlling for age
```{r, GLM of T1/T2 ratio by ADOS CSS controlling for age, echo = FALSE, include = TRUE, results='asis'}
n <-13
T1T2ratio_aparc <- TOD_Myelin_aparc[,c(10:22)]
T1T2ratio_aparc_Vars = names(T1T2ratio_aparc)
T1T2ratio_ados_glm <- lapply(1:n, function(x) lm(T1T2ratio_aparc[,x] ~ ADOS_CSS + Age, data=TOD_Myelin_aparc))
 
for (i in seq_along(T1T2ratio_aparc_Vars)) {
  cat(tab_model(T1T2ratio_ados_glm[i], dv.labels = paste(T1T2ratio_aparc_Vars[[i]]))$knitr,"\n--------\n")
}

```
<!-- ##Correlational plots of T1/T2 ratio with ADOS CSS  -->
<!-- ```{r, correlational plots T1/T2 ratio with ADOS CSS, echo = FALSE, include = TRUE} -->
<!-- ggplot(TOD_Myelin_aparc, mapping = aes(x = ADOS_CSS, y = pericalcarine_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw() -->
<!-- ``` -->

<!-- ##T1/T2 ratio by Mullen ELC, DX, and Mullen ELC by Dx interaction controlling for age, sex, and CNR  -->
<!-- ```{r, GLM of T1/T2 ratio by Mullen ELC and Dx and Mullen ELC by Dx interaction controlling for age and sex and CNR, echo = FALSE, include = TRUE, results='asis'} -->
<!-- n <-13 -->
<!-- T1T2ratio_aparc <- TOD_Myelin_aparc[,c(10:22)] -->
<!-- T1T2ratio_aparc_Vars = names(T1T2ratio_aparc) -->
<!-- T1T2ratio_mullenELC_glm <- lapply(1:n, function(x) lm(T1T2ratio_aparc[,x] ~ Mullen_ELC + Group + Age + Sex + gray_white_cnr + Mullen_ELC*Group, data=TOD_Myelin_aparc)) -->

<!-- for (i in seq_along(T1T2ratio_aparc_Vars)) { -->
<!--   cat(tab_model(T1T2ratio_mullenELC_glm[i], dv.labels = paste(T1T2ratio_aparc_Vars[[i]]))$knitr,"\n--------\n") -->
<!-- } -->

<!-- ``` -->

##T1/T2 ratio by Mullen ELC controlling for Dx and age 
```{r, GLM of T1/T2 ratio by Mullen ELC controlling for Dx and age, echo = FALSE, include = TRUE, results='asis'}
n <-13
T1T2ratio_aparc <- TOD_Myelin_aparc[,c(10:22)]
T1T2ratio_aparc_Vars = names(T1T2ratio_aparc)
T1T2ratio_mullenELC_glm_simple <- lapply(1:n, function(x) lm(T1T2ratio_aparc[,x] ~ Mullen_ELC + Group + Age, data=TOD_Myelin_aparc))
 
for (i in seq_along(T1T2ratio_aparc_Vars)) {
  cat(tab_model(T1T2ratio_mullenELC_glm_simple[i], dv.labels = paste(T1T2ratio_aparc_Vars[[i]]))$knitr,"\n--------\n")
}

```

##Correlational plots of T1/T2 ratio with Mullen_ELC 
```{r, correlational plots T1/T2 ratio with Mullen ELC, echo = FALSE, include = TRUE}

ggplot(TOD_Myelin_aparc, mapping = aes(x = Mullen_ELC, y = pericalcarine_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()
ggplot(TOD_Myelin_aparc, mapping = aes(x = Mullen_ELC, y = cuneus_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()
ggplot(TOD_Myelin_aparc, mapping = aes(x = Mullen_ELC, y = precuneus_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()

```

##T1/T2 ratio by Mullen VR controlling for Dx and age
```{r, GLM of T1/T2 ratio by Mullen VR controlling for Dx and age, echo = FALSE, include = TRUE, results='asis'}
n <-13
T1T2ratio_aparc <- TOD_Myelin_aparc[,c(10:22)]
T1T2ratio_aparc_Vars = names(T1T2ratio_aparc)
T1T2ratio_mullenVR_glm_simple <- lapply(1:n, function(x) lm(T1T2ratio_aparc[,x] ~ Mullen_VR_T + Group + Age, data=TOD_Myelin_aparc))
 
for (i in seq_along(T1T2ratio_aparc_Vars)) {
  cat(tab_model(T1T2ratio_mullenVR_glm_simple[i], dv.labels = paste(T1T2ratio_aparc_Vars[[i]]))$knitr,"\n--------\n")
}

```

##Correlational plots of T1/T2 ratio with Mullen_VR 
```{r, correlational plots T1/T2 ratio with Mullen VR, echo = FALSE, include = TRUE}

ggplot(TOD_Myelin_aparc, mapping = aes(x = Mullen_VR_T, y = pericalcarine_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()
ggplot(TOD_Myelin_aparc, mapping = aes(x = Mullen_VR_T, y = cuneus_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()

```

##T1/T2 ratio by Mullen FM controlling for Dx and age 
```{r, GLM of T1/T2 ratio by Mullen FM controlling for Dx and age, echo = FALSE, include = TRUE, results='asis'}
n <-13
T1T2ratio_aparc <- TOD_Myelin_aparc[,c(10:22)]
T1T2ratio_aparc_Vars = names(T1T2ratio_aparc)
T1T2ratio_mullenFM_glm_simple <- lapply(1:n, function(x) lm(T1T2ratio_aparc[,x] ~ Mullen_FM_T + Group + Age, data=TOD_Myelin_aparc))
 
for (i in seq_along(T1T2ratio_aparc_Vars)) {
  cat(tab_model(T1T2ratio_mullenFM_glm_simple[i], dv.labels = paste(T1T2ratio_aparc_Vars[[i]]))$knitr,"\n--------\n")
}

```

##T1/T2 ratio by CT, Dx, and CT by Dx interactions controlling for age 
```{r, GLM of T1/T2 ratio by CT Dx and CT by Dx interaction, echo = FALSE, include = TRUE, results='asis'}
n <-12
T1T2ratio_aparc <- TOD_Myelin_aparc[,c(10:21)]
T1T2ratio_aparc_Vars = names(T1T2ratio_aparc)
CT_aparc <- TOD_Myelin_aparc[,c(26:37)]
T1T2ratio_CT <- lapply(1:n, function(x) lm(T1T2ratio_aparc[,x] ~ CT_aparc[,x] + Age + Group + CT_aparc[,x]*Group, data=TOD_Myelin_aparc))
 
for (i in seq_along(T1T2ratio_aparc_Vars)) {
  cat(tab_model(T1T2ratio_CT[i], dv.labels = paste(T1T2ratio_aparc_Vars[[i]]))$knitr,"\n--------\n")
}

```

<!-- ##T1/T2 ratio by CT, Dx, and CT by Dx interactions controlling for age and TBV  -->
<!-- ```{r, GLM of T1/T2 ratio by CT Dx and CT by Dx interaction control for TBV, echo = FALSE, include = TRUE, results='asis'} -->
<!-- n <-12 -->
<!-- T1T2ratio_aparc <- TOD_Myelin_aparc[,c(10:21)] -->
<!-- T1T2ratio_aparc_Vars = names(T1T2ratio_aparc) -->
<!-- CT_aparc <- TOD_Myelin_aparc[,c(26:37)] -->
<!-- T1T2ratio_CT_tbv <- lapply(1:n, function(x) lm(T1T2ratio_aparc[,x] ~ CT_aparc[,x] + Age + Group + TBV + CT_aparc[,x]*Group, data=TOD_Myelin_aparc)) -->

<!-- for (i in seq_along(T1T2ratio_aparc_Vars)) { -->
<!--   cat(tab_model(T1T2ratio_CT_tbv[i], dv.labels = paste(T1T2ratio_aparc_Vars[[i]]))$knitr,"\n--------\n") -->
<!-- } -->
<!-- ``` -->

<!-- ##T1/T2 ratio by CT, controlling for Dx, age, sex, and CNR  -->
<!-- ```{r, GLM of T1/T2 ratio by CT, echo = FALSE, include = TRUE, results='asis'} -->
<!-- n <-12 -->
<!-- T1T2ratio_aparc <- TOD_Myelin_aparc[,c(10:21)] -->
<!-- T1T2ratio_aparc_Vars = names(T1T2ratio_aparc) -->
<!-- CT_aparc <- TOD_Myelin_aparc[,c(26:37)] -->
<!-- T1T2ratio_CT_simple <- lapply(1:n, function(x) lm(T1T2ratio_aparc[,x] ~ CT_aparc[,x] + Age + Group + Sex + gray_white_cnr, data=TOD_Myelin_aparc)) -->

<!-- for (i in seq_along(T1T2ratio_aparc_Vars)) { -->
<!--   cat(tab_model(T1T2ratio_CT_simple[i], dv.labels = paste(T1T2ratio_aparc_Vars[[i]]))$knitr,"\n--------\n") -->
<!-- } -->

<!-- ``` -->

<!-- ##T1/T2 ratio by CT in TD, controlling for age, sex, and CNR  -->
<!-- ```{r, GLM of T1/T2 ratio by CT in TD, echo = FALSE, include = TRUE, results='asis'} -->
<!-- n <-12 -->
<!-- T1T2ratio_aparc_TD <- TOD_Myelin_aparc_TD[,c(10:21)] -->
<!-- T1T2ratio_aparc_Vars = names(T1T2ratio_aparc) -->
<!-- CT_aparc_TD <- TOD_Myelin_aparc_TD[,c(26:37)] -->
<!-- T1T2ratio_CT_TD <- lapply(1:n, function(x) lm(T1T2ratio_aparc_TD[,x] ~ CT_aparc_TD[,x] + Age + Sex + gray_white_cnr, data=TOD_Myelin_aparc_TD)) -->

<!-- for (i in seq_along(T1T2ratio_aparc_Vars)) { -->
<!--   cat(tab_model(T1T2ratio_CT_TD[i], dv.labels = paste(T1T2ratio_aparc_Vars[[i]]))$knitr,"\n--------\n") -->
<!-- } -->
<!-- ``` -->

##Correlational plots of T1/T2 ratio with CT
```{r, correlational plots T1/T2 ratio with CT, echo = FALSE, include = TRUE}

ggplot(TOD_Myelin_aparc, mapping = aes(x = lingual_thickness, y = lingual_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()
ggplot(TOD_Myelin_aparc, mapping = aes(x = parahippocampal_thickness, y = parahippocampal_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()

```

##T1/T2 ratio by volume, Dx, and volume by Dx interactions controlling for age
```{r, GLM of T1/T2 ratio by volume Dx and volume by Dx interaction, echo = FALSE, include = TRUE, results='asis'}
n <-12
T1T2ratio_aparc <- TOD_Myelin_aparc[,c(10:21)]
T1T2ratio_aparc_Vars = names(T1T2ratio_aparc)
Volume_aparc <- TOD_Myelin_aparc[,c(38:49)]
T1T2ratio_volume <- lapply(1:n, function(x) lm(T1T2ratio_aparc[,x] ~ Volume_aparc[,x] + Age + Group + Volume_aparc[,x]*Group, data=TOD_Myelin_aparc))
 
for (i in seq_along(T1T2ratio_aparc_Vars)) {
  cat(tab_model(T1T2ratio_volume[i], dv.labels = paste(T1T2ratio_aparc_Vars[[i]]))$knitr,"\n--------\n")
}
```

<!-- ##T1/T2 ratio by volume, Dx, and volume by Dx interactions controlling for age and TBV  -->
<!-- ```{r, GLM of T1/T2 ratio by volume Dx and volume by Dx interaction control for TBV, echo = FALSE, include = TRUE, results='asis'} -->
<!-- n <-12 -->
<!-- T1T2ratio_aparc <- TOD_Myelin_aparc[,c(10:21)] -->
<!-- T1T2ratio_aparc_Vars = names(T1T2ratio_aparc) -->
<!-- Volume_aparc <- TOD_Myelin_aparc[,c(38:49)] -->
<!-- T1T2ratio_volume_tbv <- lapply(1:n, function(x) lm(T1T2ratio_aparc[,x] ~ Volume_aparc[,x] + Age + Group + TBV + Volume_aparc[,x]*Group, data=TOD_Myelin_aparc)) -->

<!-- for (i in seq_along(T1T2ratio_aparc_Vars)) { -->
<!--   cat(tab_model(T1T2ratio_volume_tbv[i], dv.labels = paste(T1T2ratio_aparc_Vars[[i]]))$knitr,"\n--------\n") -->
<!-- } -->

<!-- ``` -->

<!-- ##T1/T2 ratio by volume controlling for Dx, age, sex, and CNR  -->
<!-- ```{r, GLM of T1/T2 ratio by volume, echo = FALSE, include = TRUE, results='asis'} -->
<!-- n <-12 -->
<!-- T1T2ratio_aparc <- TOD_Myelin_aparc[,c(10:21)] -->
<!-- T1T2ratio_aparc_Vars = names(T1T2ratio_aparc) -->
<!-- Volume_aparc <- TOD_Myelin_aparc[,c(38:49)] -->
<!-- T1T2ratio_volume_simple <- lapply(1:n, function(x) lm(T1T2ratio_aparc[,x] ~ Volume_aparc[,x] + Age + Group + Sex + gray_white_cnr, data=TOD_Myelin_aparc)) -->

<!-- for (i in seq_along(T1T2ratio_aparc_Vars)) { -->
<!--   cat(tab_model(T1T2ratio_volume_simple[i], dv.labels = paste(T1T2ratio_aparc_Vars[[i]]))$knitr,"\n--------\n") -->
<!-- } -->

<!-- ``` -->

<!-- ##T1/T2 ratio by volume in TD controlling for age, sex, and CNR  -->
<!-- ```{r, GLM of T1/T2 ratio by volume in TD, echo = FALSE, include = TRUE, results='asis'} -->
<!-- n <-12 -->
<!-- T1T2ratio_aparc_TD <- TOD_Myelin_aparc_TD[,c(10:21)] -->
<!-- T1T2ratio_aparc_Vars = names(T1T2ratio_aparc) -->
<!-- Volume_aparc_TD <- TOD_Myelin_aparc_TD[,c(38:49)] -->
<!-- T1T2ratio_volume_TD <- lapply(1:n, function(x) lm(T1T2ratio_aparc_TD[,x] ~ Volume_aparc_TD[,x] + Age + Sex + gray_white_cnr, data=TOD_Myelin_aparc_TD)) -->

<!-- for (i in seq_along(T1T2ratio_aparc_Vars)) { -->
<!--   cat(tab_model(T1T2ratio_volume_TD[i], dv.labels = paste(T1T2ratio_aparc_Vars[[i]]))$knitr,"\n--------\n") -->
<!-- } -->

<!-- ``` -->

##Correlational plots of T1/T2 ratio with volume
```{r, correlational plots T1/T2 ratio with volume, echo = FALSE, include = TRUE}

ggplot(TOD_Myelin_aparc, mapping = aes(x = cuneus_volume, y = cuneus_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()
ggplot(TOD_Myelin_aparc, mapping = aes(x = precuneus_volume, y = precuneus_myelin, colour = Dx)) + geom_point() + geom_smooth(method='lm', formula = y~x) + theme_bw()

```
